### 2023-01-24 Strydom_et_al_2023_graph_embedding_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@769f8d08213a74eb01c156b8aa2c72a1600175b0 🚀

The popularity of graph embedding techniques in machine learning is more
than the search for structural invariants: graphs are discrete objects,
and machine learning techniques tend to handle continuous data better.
Bringing a sparse graph into a continuous, dense vector space (Xu, 2021)
opens up a broader variety of predictive algorithms, notably of the sort
that are able to predict events as probabilities (Murphy, 2022).
Furthermore, the projection of the graph itself is a representation that
can be learned; Runghen et al. (2021), for example, used a neural
network to learn the embedding of a network in which not all
interactions were known, based on the nodes' metadata. This example has
many parallels in ecology (see fig.~\ref{fig:embedding} \textbf{C}), in
which node metadata can be represented by phylogeny, abundance, or
functional traits. Using phylogeny as a source of information assumes
(or strives to capture) the action of evolutionary processes on network
structure, which at least for food webs have been well documented (Dalla
Riva \& Stouffer, 2016; Stouffer et al., 2012; Stouffer et al., 2007);
similarly, the use of functional traits assumes that interactions can be
inferred from the knowledge of trait-matching rules, which is similarly
well supported in the empirical literature (Bartomeus, 2013; Bartomeus
et al., 2016; Gravel et al., 2013). Relating this information to an
embedding rather than a list of networks measures would allow to capture
their effect on the more fundamental aspects of network structure;
conversely, the absence of a phylogenetic or functional signal may
suggest that evolutionary/trait processes are not strong drivers of
network structure, therefore opening a new way to perform hypothesis
testing.

@@

The second series of problems relate to determining which area should be
used to infer the new metaweb in, as this determines the species pool
that must be used. Metawebs can be constructed by assigning interactions
in a list of species within geographic boundaries. The upside of this
approach is that information at the country level is likely to be
required for biodiversity assessments, as countries set conservation
goals at the national level (Buxton et al., 2021), and as quantitative
instruments are designed to work at these scales (Turak et al., 2017);
specific strategies are often enacted at smaller scales, nested within a
specific country (Ray et al., 2021). But there is no guarantee that
these boundaries are meaningful. In fact, we do not have a satisfying
answer to the question of ``where does a food web stop?''; the most
promising solutions involve examining the spatial consistency of network
area relationships (Fortin et al., 2021; see \emph{e.g.} Galiana et al.,
2018, 2019, 2021), which is impossible in the absence of enough
information about the network itself. This suggests that inferred
metawebs should be further downscaled to allow for \emph{a posteriori}
analyses. The methodology for metaweb downscaling is currently limited,
and it is likely that the sustained effort to characterize the spatial
dependency of food web structure will lead to more prescriptive
guidelines about the need for prediction downscaling. Recent results by
(\textbf{Martins2022GloReg?}) suggest that networks are shaped within
eco-regions, with abrupt structural transitions from an eco-region to
the next. Should this trend hold generally, this would provide an
ecologically-relevant scale at which metawebs can be downscaled and
predicted.

The final family of problems relates less to ecological methods than to
the praxis of ecological research. Operating under the context of
national divisions, in large parts of the world, reflects nothing more
than the legacy of settler colonialism, which drives a disparity in
available ecological data. Applying any embedding to biased data does
not debias them, but instead embeds these very same biases, propagating
them to the machine learning models using embeddings to make
predictions. Indeed, the use of ecological data is not an apolitical act
(Nost \& Goldstein, 2021), as data infrastructures tend to be designed
to answer questions within national boundaries (therefore placing
contingencies on what is available to be embedded), and their use often
draws upon and reinforces territorial statecraft. As per Machen \& Nost
(2021), this is particularly true when the output of ``algorithmic
thinking'' (\emph{e.g.} relying on machine learning to generate
knowledge) can be re-used for governance (\emph{e.g.} enacting
conservation decisions at the national scale). As information on species
interaction networks structure is increasingly leveraged as a tool to
guide conservation actions {[}see \emph{e.g.} recent discussions for
food-web based conservation; Eero et al. (2021); Naman et al. (2022);
Stier et al. (2017){]}, the need to appraise and correct biases that are
unwittingly propagated to algorithms when embedded from the original
data is paramount. These considerations are even more urgent in the
specific context of biodiversity data, as long-term colonial legacies
still shape taxonomic composition to this day
(\textbf{Lenzner2022NatAli?}; \textbf{Raja2022ColSha?}), and where much
shorter-term changes in taxonomic and genetic richness emerged as a
consequence of environmental racism. (\textbf{Schmidt2022SysRac?}).

@@

\leavevmode\vadjust pre{\hypertarget{ref-Albouy2019MarFis}{}}%
Albouy, C., Archambault, P., Appeltans, W., Araújo, M. B., Beauchesne,
D., Cazelles, K., Cirtwill, A. R., Fortin, M.-J., Galiana, N., Leroux,
S. J., Pellissier, L., Poisot, T., Stouffer, D. B., Wood, S. A., \&
Gravel, D. (2019). The marine fish food web is globally connected.
\emph{Nature Ecology \& Evolution}, \emph{3}(8, 8), 1153--1161.
\url{https://doi.org/10.1038/s41559-019-0950-y}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Arsov2019NetEmb}{}}%
Arsov, N., \& Mirceva, G. (2019). \emph{Network Embedding: An Overview}.
\url{http://arxiv.org/abs/1911.11726}

\leavevmode\vadjust pre{\hypertarget{ref-Athreya2017StaInf}{}}%
Athreya, A., Fishkind, D. E., Levin, K., Lyzinski, V., Park, Y., Qin,
Y., Sussman, D. L., Tang, M., Vogelstein, J. T., \& Priebe, C. E.
(2017). \emph{Statistical inference on random dot product graphs: A
survey} (No. arXiv:1709.05454). arXiv.
\url{http://arxiv.org/abs/1709.05454}

\leavevmode\vadjust pre{\hypertarget{ref-Bartomeus2013UndLin}{}}%
Bartomeus, I. (2013). Understanding linkage rules in plant-pollinator
networks by using hierarchical models that incorporate pollinator
detectability and plant traits. \emph{PloS One}, \emph{8}(7), e69200.
\url{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0069200}

\leavevmode\vadjust pre{\hypertarget{ref-Bartomeus2016ComFra}{}}%
Bartomeus, I., Gravel, D., Tylianakis, J. M., Aizen, M. A., Dickie, I.
A., \& Bernard-Verdier, M. (2016). A common framework for identifying
linkage rules across different types of interactions. \emph{Functional
Ecology}, \emph{30}(12), 1894--1903.
\url{http://onlinelibrary.wiley.com/doi/10.1111/1365-2435.12666/full}

\leavevmode\vadjust pre{\hypertarget{ref-Bezanson2017JulFre}{}}%
Bezanson, J., Edelman, A., Karpinski, S., \& Shah, V. (2017). Julia: A
Fresh Approach to Numerical Computing. \emph{SIAM Review}, \emph{59}(1),
65--98. \url{https://doi.org/10.1137/141000671}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Chami2022MacLea}{}}%
Chami, I., Abu-El-Haija, S., Perozzi, B., Ré, C., \& Murphy, K. (2022).
Machine Learning on Graphs: A Model and Comprehensive Taxonomy.
\emph{Journal of Machine Learning Research}, \emph{23}(89), 1--64.
\url{http://jmlr.org/papers/v23/20-852.html}

\leavevmode\vadjust pre{\hypertarget{ref-Chen2017DeeMul}{}}%
Chen, D., Xue, Y., Fink, D., Chen, S., \& Gomes, C. P. (2017).
\emph{Deep Multi-species Embedding}. 3639--3646.
\url{https://www.ijcai.org/proceedings/2017/509}

\leavevmode\vadjust pre{\hypertarget{ref-Chen2017HarHie}{}}%
Chen, H., Perozzi, B., Hu, Y., \& Skiena, S. (2017). \emph{HARP:
Hierarchical Representation Learning for Networks}.
\url{http://arxiv.org/abs/1706.07845}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Dominguez2020DecCon}{}}%
Domínguez, L., \& Luoma, C. (2020). Decolonising Conservation Policy:
How Colonial Land and Conservation Ideologies Persist and Perpetuate
Indigenous Injustices at the Expense of the Environment. \emph{Land},
\emph{9}(3, 3), 65. \url{https://doi.org/10.3390/land9030065}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Fricke2022EffDef}{}}%
Fricke, E. C., Ordonez, A., Rogers, H. S., \& Svenning, J.-C. (2022).
The effects of defaunation on plants' capacity to track climate change.
\emph{Science}.
\url{https://www.science.org/doi/abs/10.1126/science.abk3510}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Galiana2019GeoVar}{}}%
Galiana, N., Hawkins, B. A., \& Montoya, J. M. (2019). The geographical
variation of network structure is scale dependent: Understanding the
biotic specialization of host--parasitoid networks. \emph{Ecography},
\emph{42}(6), 1175--1187. \url{https://doi.org/10.1111/ecog.03684}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Gravel2013InfFoo}{}}%
Gravel, D., Poisot, T., Albouy, C., Velez, L., \& Mouillot, D. (2013).
Inferring food web structure from predator-prey body size relationships.
\emph{Methods in Ecology and Evolution}, \emph{4}(11), 1083--1090.
\url{https://doi.org/10.1111/2041-210X.12103}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Grunig2020CroFor}{}}%
Grünig, M., Mazzi, D., Calanca, P., Karger, D. N., \& Pellissier, L.
(2020). Crop and forest pest metawebs shift towards increased linkage
and suitability overlap under climate change. \emph{Communications
Biology}, \emph{3}(1, 1), 1--10.
\url{https://doi.org/10.1038/s42003-020-0962-9}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Herbert1965Dun}{}}%
Herbert, F. (1965). \emph{Dune} (1st ed.). Chilton Book Company.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Jones2009PanSpe}{}}%
Jones, K. E., Bielby, J., Cardillo, M., Fritz, S. A., O'Dell, J., Orme,
C. D. L., Safi, K., Sechrest, W., Boakes, E. H., Carbone, C., Connolly,
C., Cutts, M. J., Foster, J. K., Grenyer, R., Habib, M., Plaster, C. A.,
Price, S. A., Rigby, E. A., Rist, J., \ldots{} Purvis, A. (2009).
PanTHERIA: A species‐level database of life history, ecology, and
geography of extant and recently extinct mammals: Ecological Archives
E090‐184. \emph{Ecology}, \emph{90}(9), 2648--2648.
\url{https://doi.org/10.1890/08-1494.1}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Maaten2009LeaPar}{}}%
Maaten, L. van der. (2009). Learning a Parametric Embedding by
Preserving Local Structure. \emph{Proceedings of the Twelth
International Conference on Artificial Intelligence and Statistics},
384--391. \url{https://proceedings.mlr.press/v5/maaten09a.html}

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-MoseboFernandes2020MacLea}{}}%
Mosebo Fernandes, A. C., Quintero Gonzalez, R., Lenihan-Clarke, M. A.,
Leslie Trotter, E. F., \& Jokar Arsanjani, J. (2020). Machine Learning
for Conservation Planning in a Changing Climate. \emph{Sustainability},
\emph{12}(18, 18), 7657. \url{https://doi.org/10.3390/su12187657}

\leavevmode\vadjust pre{\hypertarget{ref-Murphy2022ProMac}{}}%
Murphy, K. P. (2022). \emph{Probabilistic machine learning: An
introduction}. MIT Press. \href{https://probml.ai}{probml.ai}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Narayanan2017GraLea}{}}%
Narayanan, A., Chandramohan, M., Venkatesan, R., Chen, L., Liu, Y., \&
Jaiswal, S. (2017). \emph{Graph2vec: Learning Distributed
Representations of Graphs}. \url{http://arxiv.org/abs/1707.05005}

@@

\leavevmode\vadjust pre{\hypertarget{ref-OConnor2020UnvFoo}{}}%
O'Connor, L. M. J., Pollock, L. J., Braga, J., Ficetola, G. F.,
Maiorano, L., Martinez‐Almoyna, C., Montemaggiori, A., Ohlmann, M., \&
Thuiller, W. (2020). Unveiling the food webs of tetrapods across Europe
through the prism of the Eltonian niche. \emph{Journal of Biogeography},
\emph{47}(1), 181--192. \url{https://doi.org/10.1111/jbi.13773}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Poisot2021ImpMam}{}}%
Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M. J., Becker, D.
J., Albery, G. F., Gibb, R. J., Seifert, S. N., \& Carlson, C. J.
(2021). \emph{Imputing the mammalian virome with linear filtering and
singular value decomposition}. \url{http://arxiv.org/abs/2105.14973}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Ramasamy2015ComSpe}{}}%
Ramasamy, D., \& Madhow, U. (2015). Compressive spectral embedding:
Sidestepping the SVD. In C. Cortes, N. Lawrence, D. Lee, M. Sugiyama, \&
R. Garnett (Eds.), \emph{Advances in neural information processing
systems} (Vol. 28). Curran Associates, Inc.
\url{https://proceedings.neurips.cc/paper/2015/file/4f6ffe13a5d75b2d6a3923922b3922e5-Paper.pdf}

@@

\leavevmode\vadjust pre{\hypertarget{ref-S2013GraEmb}{}}%
S, N. S., \& Surendran, S. (2013). Graph Embedding and Dimensionality
Reduction - A Survey. \emph{International Journal of Computer Science \&
Engineering Technology}, \emph{4}(1).
\url{https://www.semanticscholar.org/paper/Graph-Embedding-and-Dimensionality-Reduction-A-Surendran/3f413d591e4b2b876e033eeb9390e232ad4826ca}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Stevenson2021AlgRis}{}}%
Stevenson, M. T., \& Doleac, J. L. (2021). \emph{Algorithmic Risk
Assessment in the Hands of Humans} (SSRN Scholarly Paper No. 3489440).
\url{https://doi.org/10.2139/ssrn.3489440}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Stouffer2007EviExi}{}}%
Stouffer, D. B., Camacho, J., Jiang, W., \& Nunes Amaral, L. A. (2007).
Evidence for the existence of a robust pattern of prey selection in food
webs. \emph{Proceedings of the Royal Society B: Biological Sciences},
\emph{274}(1621), 1931--1940.
\url{https://doi.org/10.1098/rspb.2007.0571}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Thurman2019TesLin}{}}%
Thurman, L. L., Barner, A. K., Garcia, T. S., \& Chestnut, T. (2019).
Testing the link between species interactions and co-occurrence in a
trophic network. \emph{Ecography}, \emph{0}.
\url{https://doi.org/10.1111/ecog.04360}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Wardeh2021PreMam}{}}%
Wardeh, M., Baylis, M., \& Blagrove, M. S. C. (2021). Predicting
mammalian hosts in which novel coronaviruses can be generated.
\emph{Nature Communications}, \emph{12}(1, 1), 780.
\url{https://doi.org/10.1038/s41467-021-21034-5}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Wu2021MaxPos}{}}%
Wu, D., Palmer, D. R., \& Deford, D. R. (2021). \emph{Maximum a
Posteriori Inference of Random Dot Product Graphs via Conic Programming}
(No. arXiv:2101.02180). arXiv. \url{http://arxiv.org/abs/2101.02180}

>>>>

The popularity of graph embedding techniques in machine learning is more
than the search for structural invariants: graphs are discrete objects,
and machine learning techniques tend to handle continuous data better.
Bringing a sparse graph into a continuous, dense vector space (Xu, 2021)
opens up a broader variety of predictive algorithms, notably of the sort
that are able to predict events as probabilities (Murphy, 2022).
Furthermore, the projection of the graph itself is a representation that
can be learned; Runghen et al. (2021), for example, used a neural
network to learn the embedding of a network in which not all
interactions were known, based on the nodes' metadata. This example has
many parallels in ecology (see fig.~\ref{fig:embedding} \textbf{C}), in
which node metadata can be represented by phylogeny, abundance, or
functional traits. Using phylogeny as a source of information assumes
(or strives to capture) the action of evolutionary processes on network
structure, which at least for food webs have been well documented (Dalla
Riva \& Stouffer, 2016; Stouffer et al., 2012;
\textbf{Stouffer2007EviExi?}); similarly, the use of functional traits
assumes that interactions can be inferred from the knowledge of
trait-matching rules, which is similarly well supported in the empirical
literature (Bartomeus, 2013; Bartomeus et al., 2016;
\textbf{Gravel2013InfFoo?}). Relating this information to an embedding
rather than a list of networks measures would allow to capture their
effect on the more fundamental aspects of network structure; conversely,
the absence of a phylogenetic or functional signal may suggest that
evolutionary/trait processes are not strong drivers of network
structure, therefore opening a new way to perform hypothesis testing.

@@

The second series of problems relate to determining which area should be
used to infer the new metaweb in, as this determines the species pool
that must be used. Metawebs can be constructed by assigning interactions
in a list of species within geographic boundaries. The upside of this
approach is that information at the country level is likely to be
required for biodiversity assessments, as countries set conservation
goals at the national level (Buxton et al., 2021), and as quantitative
instruments are designed to work at these scales (Turak et al., 2017);
specific strategies are often enacted at smaller scales, nested within a
specific country (Ray et al., 2021). But there is no guarantee that
these boundaries are meaningful. In fact, we do not have a satisfying
answer to the question of ``where does a food web stop?''; the most
promising solutions involve examining the spatial consistency of network
area relationships (Fortin et al., 2021; see \emph{e.g.} Galiana et al.,
2018, 2019, 2021), which is impossible in the absence of enough
information about the network itself. This suggests that inferred
metawebs should be further downscaled to allow for \emph{a posteriori}
analyses. The methodology for metaweb downscaling is currently limited,
and it is likely that the sustained effort to characterize the spatial
dependency of food web structure will lead to more prescriptive
guidelines about the need for prediction downscaling. Recent results by
Martins et al. (2022) suggest that networks are shaped within
eco-regions, with abrupt structural transitions from an eco-region to
the next. Should this trend hold generally, this would provide an
ecologically-relevant scale at which metawebs can be downscaled and
predicted.

The final family of problems relates less to ecological methods than to
the praxis of ecological research. Operating under the context of
national divisions, in large parts of the world, reflects nothing more
than the legacy of settler colonialism, which drives a disparity in
available ecological data. Applying any embedding to biased data does
not debias them, but instead embeds these very same biases, propagating
them to the machine learning models using embeddings to make
predictions. Indeed, the use of ecological data is not an apolitical act
(Nost \& Goldstein, 2021), as data infrastructures tend to be designed
to answer questions within national boundaries (therefore placing
contingencies on what is available to be embedded), and their use often
draws upon and reinforces territorial statecraft. As per Machen \& Nost
(2021), this is particularly true when the output of ``algorithmic
thinking'' (\emph{e.g.} relying on machine learning to generate
knowledge) can be re-used for governance (\emph{e.g.} enacting
conservation decisions at the national scale). As information on species
interaction networks structure is increasingly leveraged as a tool to
guide conservation actions {[}see \emph{e.g.} recent discussions for
food-web based conservation; Eero et al. (2021); Naman et al. (2022);
Stier et al. (2017){]}, the need to appraise and correct biases that are
unwittingly propagated to algorithms when embedded from the original
data is paramount. These considerations are even more urgent in the
specific context of biodiversity data, as long-term colonial legacies
still shape taxonomic composition to this day (Lenzner et al., 2022;
Raja, 2022), and where much shorter-term changes in taxonomic and
genetic richness emerged as a consequence of environmental racism.
(Schmidt \& Garroway, 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-Albouy2019MarFis}{}}%
Albouy, C., Archambault, P., Appeltans, W., Araújo, M. B., Beauchesne,
D., Cazelles, K., Cirtwill, A. R., Fortin, M.-J., Galiana, N., Leroux,
S. J., Pellissier, L., Poisot, T., Stouffer, D. B., Wood, S. A., \&
Gravel, D. (2019). The marine fish food web is globally connected.
\emph{Nature Ecology \& Evolution}, \emph{3}(8), 1153--1161.
\url{https://doi.org/10.1038/s41559-019-0950-y}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Arsov2019NetEmb}{}}%
Arsov, N., \& Mirceva, G. (2019). Network Embedding: An Overview.
\emph{arXiv:1911.11726 {[}Cs, Stat{]}}.
\url{https://arxiv.org/abs/1911.11726}

\leavevmode\vadjust pre{\hypertarget{ref-Athreya2017StaInf}{}}%
Athreya, A., Fishkind, D. E., Levin, K., Lyzinski, V., Park, Y., Qin,
Y., Sussman, D. L., Tang, M., Vogelstein, J. T., \& Priebe, C. E.
(2017). \emph{Statistical inference on random dot product graphs: A
survey} (No. arXiv:1709.05454). arXiv.
\url{https://arxiv.org/abs/1709.05454}

\leavevmode\vadjust pre{\hypertarget{ref-Bartomeus2013UndLin}{}}%
Bartomeus, I. (2013). Understanding linkage rules in plant-pollinator
networks by using hierarchical models that incorporate pollinator
detectability and plant traits. \emph{PloS One}, \emph{8}(7), e69200.

\leavevmode\vadjust pre{\hypertarget{ref-Bartomeus2016ComFra}{}}%
Bartomeus, I., Gravel, D., Tylianakis, J. M., Aizen, M. A., Dickie, I.
A., \& Bernard-Verdier, M. (2016). A common framework for identifying
linkage rules across different types of interactions. \emph{Functional
Ecology}, \emph{30}(12), 1894--1903.

\leavevmode\vadjust pre{\hypertarget{ref-Bezanson2017JulFre}{}}%
Bezanson, J., Edelman, A., Karpinski, S., \& Shah, V. B. (2017). Julia:
A Fresh Approach to Numerical Computing. \emph{SIAM Review},
\emph{59}(1), 65--98. \url{https://doi.org/10.1137/141000671}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Chami2022MacLea}{}}%
Chami, I., Abu-El-Haija, S., Perozzi, B., Ré, C., \& Murphy, K. (2022).
Machine Learning on Graphs: A Model and Comprehensive Taxonomy.
\emph{Journal of Machine Learning Research}, \emph{23}(89), 1--64.

\leavevmode\vadjust pre{\hypertarget{ref-Chen2017DeeMul}{}}%
Chen, D., Xue, Y., Fink, D., Chen, S., \& Gomes, C. P. (2017).
\emph{Deep Multi-species Embedding}. 3639--3646.

\leavevmode\vadjust pre{\hypertarget{ref-Chen2017HarHie}{}}%
Chen, H., Perozzi, B., Hu, Y., \& Skiena, S. (2017). HARP: Hierarchical
Representation Learning for Networks. \emph{arXiv:1706.07845 {[}Cs{]}}.
\url{https://arxiv.org/abs/1706.07845}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Dominguez2020DecCon}{}}%
Domínguez, L., \& Luoma, C. (2020). Decolonising Conservation Policy:
How Colonial Land and Conservation Ideologies Persist and Perpetuate
Indigenous Injustices at the Expense of the Environment. \emph{Land},
\emph{9}(3), 65. \url{https://doi.org/10.3390/land9030065}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Fricke2022EffDef}{}}%
Fricke, E. C., Ordonez, A., Rogers, H. S., \& Svenning, J.-C. (2022).
The effects of defaunation on plants' capacity to track climate change.
\emph{Science}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Galiana2019GeoVar}{}}%
Galiana, N., Hawkins, B. A., \& Montoya, J. M. (2019). The geographical
variation of network structure is scale dependent: Understanding the
biotic specialization of hostparasitoid networks. \emph{Ecography},
\emph{42}(6), 1175--1187. \url{https://doi.org/10.1111/ecog.03684}

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-Grunig2020CroFor}{}}%
Grünig, M., Mazzi, D., Calanca, P., Karger, D. N., \& Pellissier, L.
(2020). Crop and forest pest metawebs shift towards increased linkage
and suitability overlap under climate change. \emph{Communications
Biology}, \emph{3}(1), 1--10.
\url{https://doi.org/10.1038/s42003-020-0962-9}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Herbert1965Dun}{}}%
Herbert, F. (1965). \emph{Dune} (First). Chilton Book Company.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Jones2009PanSpe}{}}%
Jones, K. E., Bielby, J., Cardillo, M., Fritz, S. A., O'Dell, J., Orme,
C. D. L., Safi, K., Sechrest, W., Boakes, E. H., Carbone, C., Connolly,
C., Cutts, M. J., Foster, J. K., Grenyer, R., Habib, M., Plaster, C. A.,
Price, S. A., Rigby, E. A., Rist, J., \ldots{} Purvis, A. (2009).
PanTHERIA: A species-level database of life history, ecology, and
geography of extant and recently extinct mammals: Ecological Archives
E090-184. \emph{Ecology}, \emph{90}(9), 2648--2648.
\url{https://doi.org/10.1890/08-1494.1}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Lenzner2022NatAli}{}}%
Lenzner, B., Latombe, G., Schertler, A., Seebens, H., Yang, Q., Winter,
M., Weigelt, P., van Kleunen, M., Pyšek, P., Pergl, J., Kreft, H.,
Dawson, W., Dullinger, S., \& Essl, F. (2022). Naturalized alien floras
still carry the legacy of European colonialism. \emph{Nature Ecology \&
Evolution}, 1--10. \url{https://doi.org/10.1038/s41559-022-01865-1}

\leavevmode\vadjust pre{\hypertarget{ref-Maaten2009LeaPar}{}}%
Maaten, L. van der. (2009). Learning a Parametric Embedding by
Preserving Local Structure. \emph{Proceedings of the Twelth
International Conference on Artificial Intelligence and Statistics},
384--391.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Martins2022GloReg}{}}%
Martins, L. P., Stouffer, D. B., Blendinger, P. G., Böhning-Gaese, K.,
Buitrón-Jurado, G., Correia, M., Costa, J. M., Dehling, D. M., Donatti,
C. I., Emer, C., Galetti, M., Heleno, R., Jordano, P., Menezes, Í.,
Morante-Filho, J. C., Muñoz, M. C., Neuschulz, E. L., Pizo, M. A.,
Quitián, M., \ldots{} Tylianakis, J. M. (2022). Global and regional
ecological boundaries explain abrupt spatial discontinuities in avian
frugivory interactions. \emph{Nature Communications}, \emph{13}(1),
6943. \url{https://doi.org/10.1038/s41467-022-34355-w}

@@

\leavevmode\vadjust pre{\hypertarget{ref-MoseboFernandes2020MacLea}{}}%
Mosebo Fernandes, A. C., Quintero Gonzalez, R., Lenihan-Clarke, M. A.,
Leslie Trotter, E. F., \& Jokar Arsanjani, J. (2020). Machine Learning
for Conservation Planning in a Changing Climate. \emph{Sustainability},
\emph{12}(18), 7657. \url{https://doi.org/10.3390/su12187657}

\leavevmode\vadjust pre{\hypertarget{ref-Murphy2022ProMac}{}}%
Murphy, K. P. (2022). \emph{Probabilistic machine learning: An
introduction}. MIT Press.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Narayanan2017GraLea}{}}%
Narayanan, A., Chandramohan, M., Venkatesan, R., Chen, L., Liu, Y., \&
Jaiswal, S. (2017). Graph2vec: Learning Distributed Representations of
Graphs. \emph{arXiv:1707.05005 {[}Cs{]}}.
\url{https://arxiv.org/abs/1707.05005}

@@

\leavevmode\vadjust pre{\hypertarget{ref-OConnor2020UnvFoo}{}}%
O'Connor, L. M. J., Pollock, L. J., Braga, J., Ficetola, G. F.,
Maiorano, L., Martinez-Almoyna, C., Montemaggiori, A., Ohlmann, M., \&
Thuiller, W. (2020). Unveiling the food webs of tetrapods across Europe
through the prism of the Eltonian niche. \emph{Journal of Biogeography},
\emph{47}(1), 181--192. \url{https://doi.org/10.1111/jbi.13773}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Poisot2021ImpMam}{}}%
Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M. J., Becker, D.
J., Albery, G. F., Gibb, R. J., Seifert, S. N., \& Carlson, C. J.
(2021). Imputing the mammalian virome with linear filtering and singular
value decomposition. \emph{arXiv:2105.14973 {[}q-Bio{]}}.
\url{https://arxiv.org/abs/2105.14973}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Raja2022ColSha}{}}%
Raja, N. B. (2022). Colonialism shaped today's biodiversity.
\emph{Nature Ecology \& Evolution}, 1--2.
\url{https://doi.org/10.1038/s41559-022-01903-y}

\leavevmode\vadjust pre{\hypertarget{ref-Ramasamy2015ComSpe}{}}%
Ramasamy, D., \& Madhow, U. (2015). Compressive spectral embedding:
Sidestepping the SVD. In C. Cortes, N. Lawrence, D. Lee, M. Sugiyama, \&
R. Garnett (Eds.), \emph{Advances in neural information processing
systems} (Vol. 28). Curran Associates, Inc.

@@

\leavevmode\vadjust pre{\hypertarget{ref-S2013GraEmb}{}}%
S, N. S., \& Surendran, S. (2013). Graph Embedding and Dimensionality
Reduction - A Survey. \emph{International Journal of Computer Science \&
Engineering Technology}, \emph{4}(1).

@@

\leavevmode\vadjust pre{\hypertarget{ref-Schmidt2022SysRac}{}}%
Schmidt, C., \& Garroway, C. J. (2022). Systemic racism alters wildlife
genetic diversity. \emph{Proceedings of the National Academy of
Sciences}, \emph{119}(43), e2102860119.
\url{https://doi.org/10.1073/pnas.2102860119}

\leavevmode\vadjust pre{\hypertarget{ref-Stevenson2021AlgRis}{}}%
Stevenson, M. T., \& Doleac, J. L. (2021). \emph{Algorithmic Risk
Assessment in the Hands of Humans} (\{\{SSRN Scholarly Paper\}\} No.
3489440). \url{https://doi.org/10.2139/ssrn.3489440}

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-Thurman2019TesLin}{}}%
Thurman, L. L., Barner, A. K., Garcia, T. S., \& Chestnut, T. (2019).
Testing the link between species interactions and co-occurrence in a
trophic network. \emph{Ecography}, \emph{0}(ja).
\url{https://doi.org/10.1111/ecog.04360}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Wardeh2021PreMam}{}}%
Wardeh, M., Baylis, M., \& Blagrove, M. S. C. (2021). Predicting
mammalian hosts in which novel coronaviruses can be generated.
\emph{Nature Communications}, \emph{12}(1), 780.
\url{https://doi.org/10.1038/s41467-021-21034-5}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Wu2021MaxPos}{}}%
Wu, D., Palmer, D. R., \& Deford, D. R. (2021). \emph{Maximum a
Posteriori Inference of Random Dot Product Graphs via Conic Programming}
(No. arXiv:2101.02180). arXiv. \url{https://arxiv.org/abs/2101.02180}
